\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Adrian Silva} \\ \vspace{1pt}
    \small \href{mailto:adri4silva@gmail.com}{\underline{adri4silva@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/adri4silva}{\underline{linkedin.com/in/adri4silva}} $|$
    \href{https://github.com/adri4silva}{\underline{github.com/adri4silva}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
\justify
iOS Engineer with 6+ years of experience delivering robust applications across diverse team environments, from 2-person startups to 25+ developer organizations. Specialized in test-driven development (TDD/BDD) and functional programming paradigms (FP/FRP). Deep expertise in modern iOS frameworks including SwiftUI, UIKit, Combine, RxSwift, and ReactiveSwift, with proven proficiency in MVVM, Redux, and TCA architectures. Passionate about agile methodologies (Scrum/Kanban) and building products from concept to launch.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Engineer II}{Jun. 2022 -- Present}
      {Trade Republic}{Remote}
      \resumeItemListStart
        \resumeItem{Built core debit card functionality from scratch, including card provisioning, real-time transaction tracking, card controls, and data visualization features (spending bubbles chart)}
        \resumeItem{Contributed to launching a consumer debit card used by millions of users from concept to production, navigating complex technical challenges while ensuring seamless integration with the mobile banking platform}
        \resumeItem{Drove development of the child savings account product, used by thousands of users across Europe, leading the adaptation of savings plan flows and implementing co-parenting features to enable shared account management, delivering a seamless investment experience for families}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Developer - Senior iOS Developer}{Dec. 2020 -- Jun. 2022}
      {Hopin}{Remote}
      \resumeItemListStart
        \resumeItem{Founding member of mobile team, establishing initial iOS architecture and project structure using SwiftUI and The Composable Architecture, setting technical foundation for scalable virtual events platform}
        \resumeItem{Implemented real-time communication features including WebRTC-based video streaming, chat system, and video conferencing capabilities, enabling seamless virtual event experiences for users worldwide}
        \resumeItem{Built interactive engagement tools such as in-chat polling and engagement games, enhancing attendee participation and creating dynamic event environments from mobile devices}
      \resumeItemListEnd
      
    \resumeSubheading
      {Junior iOS Developer}{Aug. 2019 -- Dec. 2020}
      {FREENOW}{Barcelona, Spain}
      \resumeItemListStart
        \resumeItem{Developed driver engagement and incentive products for Europe's leading ride-hailing platform (14M+ passengers, 100+ cities), implementing bonus structures and rewards programs to increase driver retention and app usage across the BMW-Daimler mobility joint venture}
        \resumeItem{Modernized legacy codebase by migrating from Objective-C to Swift, implementing modularization with Tuist, and establishing functional programming patterns with custom Redux architecture and RxSwift for a scalable, maintainable solution}
        \resumeItem{Contributed across full product lifecycle from discovery and design feedback through A/B testing with Firebase/Mixpanel, working in T-shaped Spotify-model agile teams with comprehensive test coverage (UI and unit tests)}
      \resumeItemListEnd
      
    \resumeSubheading
      {iOS Developer Intern}{Apr 2018 -- Jul 2019}	
      {Quobis}{O Porriño, Spain}
      \resumeItemListStart
        \resumeItem{Developed FERMAX Blue smart home application, implementing WebRTC-based video streaming and real-time communication for remote door camera monitoring and guest interaction}
        \resumeItem{Built remote access control features enabling users to conduct video calls with visitors, unlock doors remotely, and manage home security from anywhere through iOS app}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Teaching Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {iOS Fundamentals - App Release}{Aug. 2023 -- Present}	
        {KeepCoding}{Remote}
        \resumeItemListStart
          \resumeItem{iOS Fundamentals Instructor, teaching Swift, UIKit, and Xcode basics to bootcamp students, guiding them through hands-on projects including a Spotify player clone to build foundational mobile development skills}
          \resumeItem{App Release \& CI/CD Professor, educating students on production deployment workflows using App Store Connect, Xcode Cloud pipelines, and Firebase integration for crash reporting and analytics}
          \resumeItem{Mentored aspiring iOS developers through full development lifecycle, from interface design and Swift fundamentals to automated testing, continuous integration, and App Store release best practices}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, JavaScript, Kotlin} \\
     \textbf{Technologies}{: UIKit, SwiftUI, MVVM, Combine, RxSwift, ReactiveSwift, TCA} \\
     \textbf{Tools}{: Xcode, Claude Code, Cursor} \\
    }}
 \end{itemize}
 
 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitat Oberta de Catalunya}{Remote}
      {Bachelor's Degree in Computer Engineering}{Sep. 2019 -- Jun. 2020}
    \resumeSubheading
      {KeepCoding}{Remote}
      {Mobile Engineering Bootcamp}{Jun. 2018 -- Jun. 2019}
    \resumeSubheading
      {CPR Daniel Castelao}{Vigo, Spain}
      {Higher Technician in Software Development}{Sept. 2016 -- Jun. 2018}
    \resumeSubheading
      {Univesidad Nacional de Educacion a Distancia}{Remote}
      {Bachelor's Degree in Computer Engineering}{Sept. 2016 -- Dec. 2018}
    \resumeSubheading
      {Univesidad de Vigo}{Vigo, Spain}
      {Bachelor's Degree in Electrical Engineering}{Sept. 2014 -- Jun. 2016}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
